### 2019-09-27 conflog.tex
add driving costs

>>>>

\begin{center}
   \begin{tabular}{lcccc}
   \hline\hline
   School&Estimated Mileage (mi)&Driving Time (hrs)&Estimated Fuel  Cost&Estimated Fuel Cost per Person\\
   \hline\hline
    Purdue University&90&1.68&\$21.86&\$5.47\\
    University of Cincinnati&233&\$56.60&\$14.15\\
    Air Force Institute of Technology&250&3.97&\$60.73&\$15.18\\
    University of Wisconsin&253&4.00&\$61.46&\$15.36\\
    Missouri University of Science and Technology&279&4.35&\$67.77&\$16.94\\
    University of Missouri - Columbia&291&4.48&\$70.69&\$17.67\\
    Ohio State University&302&4.77&\$73.36&\$18.34\\
    University of Michigan&345&5.27&\$83.81&\$20.95\\
    Vanderbilt University&373&5.57&\$90.61&\$22.65\\
    Iowa State University&378&5.73&\$91.82&\$22.96\\
    \hline
    Average&279&4.36&\$67.87&\$16.97

    \end{tabular} 
\end{center}
